### 2014-04-24 Response_to_R0_Reviews.tex

    \item \textit{How would limits to ARFI resolution impact the results?}

    TO DO

    \item \textit{The authors explain that gross pathology weights and axis
            measurements were affected by the presence of peri-prostatic
            tissue.  Why could the peri-prostatic tissue not be differentiated
            from the prostatic tissue in histology after processing?  Wouldn't
            this enable better gold standard axis measurements?}

    We agree that very careful dissection of the gross organ from adjacent
    peri-prostatic tissue could be achieved, but to not disrupt the clinical
    pathologic processing of these samples, we could not specify specific
    pathology assisstants to process these specimens, so there was some
    inherent variability associated with the time and effort that each
    assistant dedicated to removing this peri-prostatic tissue.  We felt that
    it was important to delineate this as a source of variability among our
    pathology specimens, though it is expected to be a higher-order source of
    error.

### 2014-04-24 Response_to_R0_Reviews.tex

    \item \textit{The authors explain that gross pathology weights and axis
            measurements were affected by the presence of peri-prostatic
            tissue.  Why could the peri-prostatic tissue not be differentiated
            from the prostatic tissue in histology after processing?  Wouldn't
            this enable better gold standard axis measurements?}

    We agree that very careful dissection of the gross organ from adjacent
    peri-prostatic tissue could be achieved, but to not disrupt the clinical
    pathologic processing of these samples, we could not specify specific
    pathology assisstants to process these specimens, so there was some
    inherent variability associated with the time and effort that each
    assistant dedicated to removing this peri-prostatic tissue.  We felt that
    it was important to delineate this as a source of variability among our
    pathology specimens, though it is expected to be a higher-order source of
    error.

    \item \textit{Further to the point above, if the prostatic tissue axes
            could be measured after histological processing, could you perform
            an ROC analysis to assess ARFI/B-Mode versus MRI performance for
            axis measurement?}

    As is also detailed in the response to comment 2 by the second reviewer, we
    are actively pursuing correlation of our B-mode/ARFI and MR images with
    whole mount histology, which includes rigid and diffeomorphic image
    registration processes.  Given the that the methods and validation
    associated with the more spatially-refined whole mount histology analysis
    and diffeomorphic image registration is nontrivial, we have decided to
    present that material in a dedicated manuscript that will allow us to
    present our validation of that methodology.

### 2014-04-24 Response_to_R0_Reviews.tex

    Sagittal B-mode and ARFI ultrasound image stacks were segmented in 3D
    Slicer \textbf{by two researchers (TJG \& ZAM)}\ldots

    \textbf{All B-mode and ARFI image segmentations were reviewed by an
        experienced ARFI imaging researcher (KRN).}

    \item \textit{How would limits to ARFI resolution impact the results?}

    ARFI resolution within a native imaging frame is not considered a limiting
    factor in our ability to delineate the prostate central glands since the
    scan-conversion and slice decimation introduce resolution distortions that
    are at least an order-of-magnitude larger than our native image plane
    resolution.  ARFI image resolution would be a more realistic limiting
    factor if we were using those primary imaging frames for exclusive gland
    delineation, but our use of the 3 orthogonal planes for segmentation makes
    this resolution of higher-order parameter.  We have added to the following
    text to Section V to emphasize this point to the reader:

    \input{arfi_resolution}

@@

    Given the reasons above, we decided to use the tri-axial measurements in
    gross pathologic evaluation as our closest approximation of the glands
    total volume as it would have been during MR and ultrasound imaging.  We
    have added text to Section II.B that details this choice for estimating our
    prostate volumes:

    \textbf{\input{path_volume_choice}}

    \item \textit{Image registration. The three orthogonal dimensions of the
            images do not mean much. The slice thickness in MRI causes
            significant errors along this measurement axis, while the
            lateral-to-lateral dimension in ARFI seems to be enlarged by the
            TRUS deformation (this is not mentioned in the discussion, but
            seems to be fairly obvious from Fig. 2 and 5, for example). A
            Jaccard index type of comparison would be preferable after rigid or
            possibly volume-preserving deformable registration.}

    We completely agree with the author that a more direct comparison of
    B-mode/ARFI imaging data with MR after ``unwrapping'' the deformation to
    register the images with one another would be more complete and satisfying,
    but two of the primary objectives of this work were (1) to compare prostate
    appearance and size in each native imaging, as would be seen by a clinician
    in each setting, and (2) to quantify the differences in the sizes of each
    dimension without the image registration to allow a clinician to
    cognitively register the images with known amounts of bias in each
    dimension.

    We are actively working on analyses that are focusing on comparing each
    imaging modality with whole mount histology as a gold standard, and then
    utilizing diffeomorphic image registration to spatially align each image
    for fused image guidance.  Both of these efforts require dedicated
    metholodology description, and more importantly, method validation and
    error analysis that, in our opinions, warrant dedicated publications to be
    thoroughly presented to readers.

    In the context of the analysis that we have presented in this manuscript
    and your comment about TRUS deformation, we have expanded our comments
    about this deformation and its impact on the results, along with more
    description of the future analysis efforts.

    Section V(A):

    \input{disc_deformation}

    And Section V(C):

    \input{future_diffeomorphic}

### 2014-04-24 disc_arfi_mr.tex
final responses in place; still need to spell check and proof read

We did not expect perfect agreement between MR and \textbf{ultrasound} imaging
volumes or tri-axial dimensions since each modality applies a different amount
of external compression to the rectal wall, which then deforms the prostate.
The endorectal coil places pressure on the prostate that is dependent on the
patient's anatomy and overall prostate size, while pressure on the prostate
during ultrasound imaging is modulated by the urologist when the transducer
rotation apparatus is locked into position prior to imaging.  The differential
deformation of the prostate can be easily visualized during the transducer
alignment process during ultrasound imaging.  It was our goal to apply as
little pressure while still maintaining uniform contact throughout the
ultrasound image acquisition. This is critical since poor acoustic coupling to
the prostate through the rectal wall can greatly diminish ARFI image
displacement SNR.

@@

>>>>

\input{disc_deformation}

@@

\input{arfi_resolution}

### 2014-04-24 future.tex
final responses in place; still need to spell check and proof read

\subsection{Future Directions}
Future directions for our research include deeper analysis of our findings,
especially the lateral dimension over-estimation, to improve our anatomic
delineation and assess further its clinical impact.  Technological improvements
to improve anterior prostate boundary delineation in both B-mode and ARFI
imaging are also being pursued for better visualization in this region.  3D
models of the prostate and central glands will be used across ARFI and MR
imaging datasets to spatially register them to facilitate correlation of
regions of PCa suspicion between the two modalities, and to correlate with
whole-mount histology of the excised prostate specimens.  This effort will
allow the sensitivity and specificity of each imaging modality for PCa
detection and characterization to be quantified.  Additionally, we will be
pursuing quantitative measurement of the pressure being applied during imaging
to help reduce prostate deformation and reduce the impact of prostate stiffness
nonlinearity in our displacement images.  While ARFI imaging of the prostate is
a constantly evolving technology, the fact that one can view the different
prostatic zones on ARFI images in addition to MRI is encouraging and could lead
to targeted diagnostic biopsies and therapies with real-time imaging for men
with PCa.

>>>>

\subsection{Future Directions}
Future directions for our research include deeper analysis of our findings,
especially the lateral dimension over-estimation, to improve our anatomic
delineation and assess further its clinical impact.  Technological improvements
to improve anterior prostate boundary delineation in both B-mode and ARFI
imaging are also being pursued for better visualization in this region.  3D
models of the prostate and central glands will be used across ARFI and MR
imaging datasets to spatially register them to facilitate correlation of
regions of PCa suspicion between the two modalities, and to correlate with
whole-mount histology of the excised prostate specimens.  
\input{future_diffeomorphic}
These
efforts for improved imaging performance and multi-modality image registration
will allow for the quantification of sensitivity and specificity of a combined
MR/B-mode/ARFI imaging system for PCa detection and characterization.
Additionally, we will be pursuing quantitative measurement of the pressure
being applied during imaging to help reduce prostate deformation and reduce the
impact of prostate stiffness nonlinearity in our displacement images.  While
ARFI imaging of the prostate is a constantly evolving technology, the fact that
one can view the different prostatic zones on ARFI images in addition to MRI is
encouraging and could lead to targeted diagnostic biopsies and therapies with
real-time imaging for men with PCa.
